DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-05-23 2015CompleteDerivation/completeDerivation.tex
Minor improvements on function spaces

As we combine parts, or increase the amount of material in each part, the total amount of material found will have to be consistent with those operations. That is: $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$. For a proper state, one that is not the difference of two states, we will expect a positive amount of material. So, if a density $\rho_\mathcal{c}$ is positive everywhere, then the total amount is also positive. This makes $\Lambda_U$ a positive linear functional. As the amount of material we will measure is always finite, the functional applied to any composite state $\mathcal{c}$ over any set $U$ will be finite.

@@

As we identified the set of Lebesque integrable continuous functions $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, it's useful to briefly show how other commonly used function spaces do not fit the bill. The set of continuous functions $C(\mathcal{S})$ would include functions that diverge at infinity. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude Gaussians. The set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ includes functions whose integral is infinite. Schwartz space $S(\mathcal{S})$ excludes functions that are not infinitely smooth which we don't have a physical argument for. The set of Lebesgue integrable functions $L^1(\mathcal{S})$ includes discontinuous functions that for \ref{continuous_map} are unphysical.

>>>>

As we combine parts, or increase the amount of material in each part, the total amount of material found will have to be consistent with those operations. That is: $\Lambda_U(a_1 \mathcal{c}_1 + a_2 \mathcal{c}_2) = a_1 \Lambda_U(\mathcal{c}_1) + a_2 \Lambda_U(\mathcal{c}_2)$. For a proper state, one that is not the difference of two states, we will expect a positive amount of material. So, if a density $\rho_\mathcal{c}$ is positive everywhere, then the total amount is also positive. This makes $\Lambda_U$ a positive linear functional. As the amount of material we measure is always finite, the functional applied to any composite state $\mathcal{c}$ over any set $U$ will be finite.

@@
